Correlation among smart grid actors

### 2015-07-23 Article.tex
some updates

In this paper, we focus on these "\textit{nodes}" in the distribution network that can produce and consume electricity. More precisely, we consider a set of agents that can be seen as aggregators of renewable distributed energy ressources (DER) and electrical loads. The production of an agent can be, of course, used to meet its own demand, but in cases where it is over-producing, we consider that it has the possibility to inject, against financial compensation, its extra-production in the grid. Such an agent model is known as a "\textit{prosumer}" \cite{Rathnayaka2012} (and will be called accordingly in this paper). The primary objective of this work is to mix the interests of the grid operator with the ones of the prosumers in a single utility function. While the latters intend to maximize their benefits with higer production contracts, the operator primary concerns are linked to the quality and stability of the injections. The coalitions that we wish to form should thus be both stable and productive as to satisfy both parts. This compromise can be difficult to obtain in real situations, especially when renewable generation and complex spatiotemporal correlation relationships come into play.

@@

The intermittent nature of renewables such as wind or solar power introduces new challenges in control design. On the contrary to fossil plants whose production can be scheduled in advance to meet the expected consumption, renewables by definition only produce when the natural ressource is present. Unfortunately, these moments do not necessarily coincide with the consumption peak hours \cite{Milligan2010}. A first approach to remedy this situation by acting on the consumption component is the use of dynamic ectricity prices sent to the end users. Together with demand side management techniques implemented on the smart meters, they consitute a first tool for shaping the consumption profiles \cite{Milligan2010}. In periods when the production is expected to be greater than the consumption, prices are scheduled low in order to encourage end users to delay their elastic loads to these periods. On the contrary, when the production is expected to be less than the consumption, high prices are scheduled to deter any delayable loads over these periods.

@@

An efficient portfolio of assets and a clustering of assets based on the correlations are obviously two very distinct things. And none of them is exactly what we seek. We will see in section X, how we combined both theories in order to form sufficiently producing coalitions with an acceptable volatility level.

@@

An essential component of the smart grid is the smart meter which makes the interface between the end user and the rest of the system. Smart meters coupled with sensors measure quantities of interest (like instantaneous consumption), receive informations from the grid (electricity price for instance), and take actions accordingly (demand side management program). Smart meters are currently and gradually deployed, and will probably provide interesting datasets to work on. Unfortunately, at the time this paper was written, production and consumption data for prosumers over a large region were not yet available to our knowledge. Some interesting experiments are notwithstanding being conducted and data are progressively made public [].

@@

Figure \ref{fig:histo_cliques} shows the distributions of the utility values for cliques of size 3 (triangles) in $ G_{2}^{\epsilon^{\star}} $ and for all the other possible triplets of agents. It is clearly visible that cliques tend to exhibit higher utilities because of their de-correlation property. Choosing cliques in $ G_{2}^{\epsilon^{\star}} $ as coalitions seems therefore appealing. Nevertheless, the quality of the results seems to decrease as the sizes of the cliques increase. Indeed, the larger the desired cliques, the more dense $ G_{2}^{\epsilon^{\star}} $ becomes (see equation \ref{epsilon_star}). There is a point where cliques results more from noisy edges than true de-correlation relationships, which decreases the quality of the results.

@@

\subsubsection{Wind power curve}
Power curves are functions that, for a given type of generator, map the input to the output power. For windturbines and solar arrays these functions are well studied and approximations have been proposed \cite{Lydia2014} \cite{Dans2007}. For the wind turbines, the power curve can be specified by 4 values :

>>>>

In this paper, we focus on these "\textit{nodes}" in the distribution network that can produce and consume electricity. More precisely, we consider a set of agents that own both renewable distributed energy ressources (DER) and electrical loads. The production of an agent can be, of course, used to meet its own demand, but in cases where it is over-producing, we consider that it has the possibility to inject, against financial compensation, its extra-production in the grid. Such an agent model is known as a "\textit{prosumer}" \cite{Rathnayaka2012} (and will be called accordingly in this paper). The primary objective of this work is to mix the interests of the grid operator with the ones of the prosumers in a single utility function. While the latters intend to maximize their benefits with higer production contracts, the operator primary concerns are linked to the quality and stability of the injections. The coalitions that we wish to form should thus be both stable and productive as to satisfy both parts. This compromise can be difficult to obtain in real situations, especially when renewable generation and complex spatiotemporal correlation relationships come into play.

@@

The intermittent nature of renewables such as wind or solar power introduces new challenges in control design. On the contrary to fossil plants whose production can be scheduled in advance to meet the expected consumption, renewables by definition only produce when the ressource is present. Unfortunately, these moments do not necessarily coincide with the consumption peak hours \cite{Milligan2010}. A first approach to remedy this situation by acting on the consumption component is the use of dynamic ectricity prices sent to the end users. Together with demand side management techniques implemented on the smart meters, they consitute a first tool for shaping the consumption profiles \cite{Milligan2010}. In periods when the production is expected to be greater than the consumption, prices are scheduled low in order to encourage end users to delay their elastic loads to these periods. On the contrary, when the production is expected to be less than the consumption, high prices are scheduled to deter any delayable loads over these periods.

@@

@@

An essential component of the smart grid is the smart meter which makes the interface between the end user and the rest of the system. Smart meters coupled with sensors measure quantities of interest (like instantaneous consumption), receive informations from the grid (electricity prices for instance), and take actions accordingly (demand side management programs). Smart meters are currently and gradually deployed, and will probably provide interesting datasets to work on. Unfortunately, at the time this paper was written, production and consumption data for prosumers over a large region were not yet available to our knowledge. Some interesting experiments are notwithstanding being conducted and data are progressively made public \cite{ISSDA}.

@@

Figure \ref{fig:histo_cliques} shows the distributions of the utility values for cliques of size 3 (triangles) in $ G_{2}^{\epsilon^{\star}} $ and for all the other possible triplets of agents. It is clearly visible that cliques tend to exhibit higher utilities because of their de-correlation property. Choosing cliques in $ G_{2}^{\epsilon^{\star}} $ as coalitions seems therefore appealing. Nevertheless, the quality of the results seems to decrease as the sizes of the cliques increase. Indeed, the larger the desired cliques, the more dense $ G_{2}^{\epsilon^{\star}} $ becomes (see equation \ref{epsilon_star}). There is a point where cliques results more from noisy edges than true de-correlation, which decreases the quality of the results.

@@

\subsubsection{Wind power curve}
Power curves are functions that, for a given type of generator, map some input quantity to the output power produced. For windturbines and solar arrays these functions are well studied and approximations have been proposed \cite{Lydia2014} \cite{Dans2007}. For the wind turbines, the power curve can be specified by 4 values :
